---
title: "Get started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Philosophy}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Example of a t-test

Before we get started lets load the three packages we need.

```{r setup, message=FALSE, warning=FALSE}
library(inductive)
library(magrittr)
library(purrr)
```

Within the `inductive` package there is a data set called [big_five](https://j3ypi.github.io/inductive/reference/big_five.html), which can be loaded with the `data()` function without further arguments when the `library()` call was executed before.

```{r}
data(big_five)
```

```{r, echo = FALSE}
big_five %>%  
  head() %>%  
  knitr::kable() 
```

There are three different ways to conduct Student’s t-Test in the inductive package. Note that all the information provided for the t-test can be applied to any other function from the package. Lets say we want to investigate whether there is a difference between the average degree of the big five personality trait *extraversion* compared to *neuroticism*. The recommend way of passing those columns to the function is the formula syntax, which is well-known from base R functions within the `stats` package like `lm()` or `aov()`. Up until now you could only use the formula syntax for a t-test when you pass a grouping variable like gender as a second argument. Now it can be used with two metrical columns as well. All arguments from `stats::t.test()` can be passed to `sta_t()`. To conduct a t-test and not a Welch test one has to set the `var.equal` argument to `TRUE`.  

```{r}
big_five %>% 
  sta_t(Extraversion ~ Neuroticism, var.equal = TRUE)
```

The option to use the formula syntax with a grouping variable still exists. The function is more strict though, so that the grouping variable must be a factor and not just a string. 

```{r, eval=FALSE}
big_five %>% 
  sta_t(Extraversion ~ Gender)
```

For those who prefer the known way of passing the columns as `x` and `y` separately, this option is included as well. 

```{r, eval=FALSE}
big_five %>% 
  sta_t(x = Extraversion, y = Neuroticism) 
```

Even the way of passing the arguments without a data argument as a vector to the function (e.g. with the dollar-operator) works exactly like it does for the corresponding base R functions from the `stats` package.

```{r, eval=FALSE}
sta_t(x = big_five$Extraversion, y = big_five$Neuroticism)
```

Note that the formula syntax will always be preferred. If the `data` is provided alongside the `formula` argument, `x` and `y` are ignored even when they are passed to function additionally. Other combinations which are not shown above will result in an error. 

## The `obj` argument

The only thing you see when you conduct a statistical test in the `inductive` package is a clean result table. But behind the scenes all functions return a list with two elements by default. To illustrate that lets save the results from above to the variable `res`.  

```{r}
res <- big_five %>% 
  sta_t(Extraversion ~ Neuroticism, var.equal = TRUE)
```

Now we can inspect those two elements with `purrr`'s function `pluck()` where one could either pass numbers (element `1` or `2`) or the name of the list elements (`result`, `obj`). 

```{r}
res %>% 
  pluck("result")
```

Of course, one could also use the dollar-operator or `[[` to access those list elements. The first element `result` contains the `data.frame` and the second element `obj` the object returned by the function from the `stats` package the function is wrapped around (e.g. `stats::t.test()`). 

```{r}
res %>% 
  pluck("obj")
```

There are certain scenarios where the default output of the `obj` element comes in handy. For example to conduct post-hoc tests after the calculation of an ANOVA or when you want to return additional fit indices like information criteria from you linear model with `broom::glance()`. To avoid this behavior and to save only the result table, one would need to set the `obj` argument to `FALSE`, which is practical e.g. when working with `tidyr::nest()` and `purrr::map`, if the objects are extremely large or if you want export the result table to LaTeX with `xtable::xtable()` or to Word with [rMarkdown](https://rmarkdown.rstudio.com/).

```{r}
big_five %>% 
  sta_t(Extraversion ~ Neuroticism, obj = FALSE) %>% 
  class()
```

All functions return the result with an additional `stats` class, which is only necessary for the adapted generic print method and can be ignored otherwise. 















