---
title: "Get started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Philosophy}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Example of a t-test

Before we get started lets load the three packages we need.

```{r setup, message=FALSE, warning=FALSE}
library(inductive)
library(magrittr)
library(purrr)
```

Within the `inductive` package there’s a data set called [big_five](https://j3ypi.github.io/inductive/reference/big_five.html).

```{r}
data(big_five)
```

```{r, echo = FALSE}
big_five %>%  
  head() %>%  
  knitr::kable() 
```

There three different ways to conduct Student’s t-Test in the inductive package. Note that all the information provided for the t-test can be applied to any other function from the package. Lets say we want to investigate whether there is a difference between the average degree of the *big5* personality trait extraversion compared to neuroticism. The recommend way of passing those columns to the function is the formula syntax, which is well-known from base R functions like `lm()` or `aov()`. Up until now you could only use the formula syntax for a t-test when you have one grouping variable like gender. To conduct a t-test and not a Welch test one has to set the `var.equal` argument to `TRUE`.  

```{r}
big_five %>% 
  sta_t(Extraversion ~ Neuroticism, var.equal = TRUE)
```

The option to use the formula syntax with a grouping variable still exists. The function is more strict though, so that the grouping variable must be a factor and not just a string. 

```{r, eval=FALSE}
big_five %>% 
  sta_t(Extraversion ~ Gender)
```

For those who prefer the known way of passing the columns as `x` and `y` separately, this option is included as well. 

```{r, eval=FALSE}
big_five %>% 
  sta_t(x = Extraversion, y = Neuroticism) 
```

Even the way of passing the arguments without a data argument to the function (e.g. with the dollar-operator) works exactly like it does for the corresponding base R functions from the `stats` package `t.test()`.

```{r, eval=FALSE}
sta_t(x = big_five$Extraversion, y = big_five$Neuroticism)
```

## The `obj` argument

The only thing you see when you conduct a test is the clean result table. But behind the scenes all functions return a list with two elements by default. To illustrate that lets save the results from above to the variable `res`.  

```{r}
res <- big_five %>% 
  sta_t(Extraversion ~ Neuroticism)
```

No we can inspect those two elements with `purrr`'s function `pluck()` where one could either pass numbers (element `1` or `2`) or the name of the list elements (`result`, `obj`). 

```{r}
res %>% 
  pluck("result")
```

Of course you could also use the dollar-operator or `[[` to access those list elements. As you see the object is the usual result from `t.test.()`. There are certain scenarios when the default output of the `obj` element comes in handy. For example to conduct post-hoc tests after the calculation of an ANOVA or when you want to return additional fit indices like information criteria from you linear model with `broom::glance()`.  

```{r}
res %>% 
  pluck("obj")
```

To avoid this behavior and to save the result table exclusively one would only need to set the `obj` argument to `FALSE`, which might come in handy when working with `purrr::map` and `tidyr::nest()` or if the objects are extremely large.

```{r}
big_five %>% 
  sta_t(Extraversion ~ Neuroticism, obj = FALSE)
```

















